Non-word repetition in Yélî Dnye

### 2020-12-21 manuscript.Rmd
update to-do notes

---
title             : "Non-word repetition in Yélî Dnye"
shorttitle        : "NWR in Yélî Dnye"

@@

- check again if all fields are explained
- set up OSF (or revise if already there)
- implement decisions on prop phones & patterns nwr mp
- revise bullet points for discussion

@@

<!--
- double check my frequency entries in segments.xlsx using the search function in https://phoible.org/parameters; take a look at http://phoible.github.io/conventions/ in case you see something about double articulation (I didn't find tp or lBj)
-->
<!--M2A: Done! Left for AC to review in segments-20201123.xlsx and, if she is satisfied, to integrate :)-->
- draft discussion

@@

<!--M2A: I think a nice way to end this bit would be very briefly (~1-sentence) linking this input scenario to the relevance of looking at NWR (à la Cristia 2020 DevRev). What do you think?-->
<!-- a2m maybe we want to bring that up in the discussion? I haven't found a good place to introduce that paper, in part because right now we have these three purposes that seem sort of unconnected with the goals of that paper... -->

>>>>

---
title             : "Non-word repetition in Yélî Dnye"
shorttitle        : "NWE in Yélî Dnye"

@@

- check again if all fields are explained
- set up OSF (or revise if already there)
- implement decisions on prop phones & patterns nwr mp
<!--Added by MC on 21 Dec 2020-->
- check and accept/deny MC's updated segment frequencies
- re-run analyses w/ new frequencies and check that outcomes didn't qualitatively change
- check YD data in figure 1 (the effect of item length looks reversed)
- see MC comments throughout and delete now-irrelevant things

@@

<!--
- double check my frequency entries in segments.xlsx using the search function in https://phoible.org/parameters; take a look at http://phoible.github.io/conventions/ in case you see something about double articulation (I didn't find tp or lBj)

M2A: Done! Left for AC to review in segments-20201123.xlsx and, if she is satisfied, to integrate :)
-->
<!--
- draft discussion

M2A: Done! I left some space for you to fill in references in a few spots since it seemed from the notes you left that you had some specific ones in mind.
-->

@@
